Hardware-Accelerated Rendering of Intersecting Volumes using Boolean Operations

### 2013-06-23 paper.tex
Don't indent all of XML listing
Fixed misspelling of 'herein' in abstract (ref #18)
Abstract focuses more on slicing method (ref #18)

% ========
% Abstract
% ========
\begin{abstract}
Rendering intersecting volumes is problematic because the renderer must
alternate between sampling from each volume to achieve the correct blending.
Methods for rendering an arbitrary number of intersecting volumes using hardware
acceleration have been developed, but they generally require a large amount of
geometry to be created every frame.  In the simple case where two axis-aligned
volumes intersect, it is shown that Boolean operations can be used so that
the camera may move without regenerating any geometry.  Furthermore, samples
that do not contribute to the final image may be completely avoided.  The two
variations presented herin achieve higher frame rates than the traditional
slicing method.
\end{abstract}

>>>>

% ========
% Abstract
% ========
\begin{abstract}
Rendering intersecting volumes is problematic because the renderer must
alternate between sampling from each volume to achieve the correct blending.
Unfortunately the traditional method for rendering intersecting volumes using
hardware acceleration requires a large amount of geometry to be created every
frame.  In the simple case where two axis-aligned volumes intersect, it is shown
that Boolean operations can be used so that the camera may move without
regenerating any geometry.  Furthermore, samples that do not contribute to the
final image may be completely avoided.  The two variations presented herein
achieve higher frame rates than the traditional slicing method.
\end{abstract}
